---
title: "Digital Economics PS1"
author: "Mason Ross Hayes"
institution: Toulouse School of Economics
output: pdf_document
---
```{r load-packages, include=FALSE}
library(tidyverse)
library(lfe)
library(tidymodels)
```
# Part 1


## Question 1

```{r, echo = FALSE}
q5_model %>% tidy() %>% kable()
```



# Part 2

## Question 1

The treated group is patent classes where there exist some German-filed patents, and the control is the patent classes without German-filed patents. The treated group covers 284 out of 399 class IDs (71.2%). 


We are told that "ways of mass producing indigo dyes were pioneered by German chemists in the early years of the 20th century" &mdash; maybe it is not right to assume that these groups are the same. German chemists or manufacturers could have some particular advantage in this domain that may even change over time differently than in the USA. Also, maybe the US specialized in different patent classes for a reason specific to some characteristics of the USA or of USA companies or individuals.

## Question 2 

The treated group and control groups look relatively similar, with 159 patents filed in the control and 204 in the treated group. Before treatment, the treated and control group are closer to being equal. 


After the TWEA law was passed, patent filings in both the treatment and the control group went up. And, this increased more in the treated group than in the control. 

The number of German-filed patents also went up after the passing of the TWEA. This may be because all patents filed pre-1919 were now invalid in the US; we would expect German firms then to re-file different, updated patents post-1919 (when the war ended, and after which the TWEA would not apply to newly-filed patents).

\begin{table}[!htbp] \centering 
  \caption{Ten Year Patent Filings, US and DE} 
  \label{q2_table_b} 
\begin{tabular}{@{\extracolsep{5pt}} ccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & TWEA Passed & Treated Group & Mean US & SD US & Count US & Mean DE & SD DE & Count DE \\ 
\hline \\[-1.8ex] 
1 & 0 & 0 & 0.029 & 0.169 & 29 & 0 & 0 & 0 \\ 
2 & 0 & 1 & 0.024 & 0.159 & 24 & 0.242 & 0.972 & 244 \\ 
3 & 1 & 0 & 0.33 & 0.578 & 130 & 0 & 0 & 0 \\ 
4 & 1 & 1 & 0.446 & 1.483 & 180 & 0.535 & 0.927 & 216 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}


## Question 3
\begin{table}[!htbp] \centering 
  \caption{Linear Model (no FE)} 
  \label{table3.1} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & Ten Year Count USA \\ 
\hline \\[-1.8ex] 
 twea\_passed & 0.301$^{***}$ \\ 
  & (0.037) \\ 
  & \\ 
 treated\_group & $-$0.006 \\ 
  & (0.028) \\ 
  & \\ 
 did & 0.121$^{**}$ \\ 
  & (0.052) \\ 
  & \\ 
 Constant & 0.029 \\ 
  & (0.020) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,793 \\ 
R$^{2}$ & 0.067 \\ 
Adjusted R$^{2}$ & 0.066 \\ 
Residual Std. Error & 0.620 (df = 2789) \\ 
F Statistic & 67.164$^{***}$ (df = 3; 2789) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 



\begin{table}[!htbp] \centering 
  \caption{Linear Model (FE)} 
  \label{table3.2} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & Ten Year Count USA \\ 
\hline \\[-1.8ex] 
 did & 0.121$^{**}$ \\ 
  & (0.049) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,793 \\ 
R$^{2}$ & 0.287 \\ 
Adjusted R$^{2}$ & 0.166 \\ 
Residual Std. Error & 0.585 (df = 2387) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 



In Table 2, we find that the coefficient of treated group is not different from zero, but that that of the treatment time (passing of TWEA), is positive and significant. This could just mean that over that period, patent filings in the US were on the rise. The DiD coefficient gives us more insight, indicating that over that same treatment period, patent filings increased more for treated firms compared to control. This is precisely the number we get by calculating it from Table 1: $0.446 - 0.330 - (0.024-0.029) = 0.121$. This coefficient is significant at the 5% level. 

By adding `class_id` and `ten_yr` fixed effects, the results do not change. This is expected, since `treated_group` is an indicator function of `class_id` and `twea_passed` is an indicator function of `ten_yr`. 


## Question 4

This data and these results imply nothing about the effects of removing copyrights, as these are industrial or technical patents and not copyrights.

These results seem to suggest that more patents were filed in the US post-1919, when the TWEA lost effect on newly-filed German patents but remained in effect on patents filed pre-1919. More importantly, the results suggest that this increase in patent filings was higher for treated class IDs than for control IDs -- in patent classes were there were German-filed patents, the number of US-filed patents increased more over the same period of time. 

On average, for treated class IDs, $0.121$ more patents were filed in the USA post-TWEA than were filed in the USA pre-TWEA. There is no evidence that the two groups were statistically different before the law was introduced. 

## Question 5

From Table 4, I find the effects for the 1920-1930 period are lower than for the 1930-1940 period:

$$
\hat Z = \dfrac{\hat \beta_{1920,y} - \hat \beta_{1930,y}}{\sqrt{SE(\hat \beta_{1920,y}^2) + SE(\hat \beta_{1930,y}^2)}} = -4.99
$$

where $\hat \beta_{year, y}$ indicates the coefficient for treated ($y = yes$) groups in $year$.

\begin{table}[!htbp] \centering 
  \caption{Treatment Effects by Year} 
  \label{table5.1} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & Ten Year Count USA \\ 
\hline \\[-1.8ex] 
 treated\_group &  \\ 
  &  \\ 
  & \\ 
 ten\_yr1880 & 0.030 \\ 
  & (0.059) \\ 
  & \\ 
 ten\_yr1890 & $-$0.000 \\ 
  & (0.059) \\ 
  & \\ 
 ten\_yr1900 & 0.005 \\ 
  & (0.059) \\ 
  & \\ 
 ten\_yr1910 & 0.036 \\ 
  & (0.059) \\ 
  & \\ 
 ten\_yr1920 & 0.107$^{*}$ \\ 
  & (0.059) \\ 
  & \\ 
 ten\_yr1930 & 0.523$^{***}$ \\ 
  & (0.059) \\ 
  & \\ 
 treated\_group:ten\_yr1880 & $-$0.021 \\ 
  & (0.083) \\ 
  & \\ 
 treated\_group:ten\_yr1890 & $-$0.010 \\ 
  & (0.083) \\ 
  & \\ 
 treated\_group:ten\_yr1900 & $-$0.0001 \\ 
  & (0.083) \\ 
  & \\ 
 treated\_group:ten\_yr1910 & $-$0.021 \\ 
  & (0.083) \\ 
  & \\ 
 treated\_group:ten\_yr1920 & 0.027 \\ 
  & (0.083) \\ 
  & \\ 
 treated\_group:ten\_yr1930 & 0.195$^{**}$ \\ 
  & (0.083) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,793 \\ 
R$^{2}$ & 0.289 \\ 
Adjusted R$^{2}$ & 0.166 \\ 
Residual Std. Error & 0.585 (df = 2382) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

The strongest effects take place in 1930; this is when there is the greatest increase in US-filed patents among both treated and non-treated groups, and with the largest difference for treated groups.

## Question 6

From the "placebo" DiD regressions in Tables 5 and 6, the DiD coefficient is not different from zero. In Table 5, I regress `Ten Year Count USA` using the presence of French-filed patents in a subclass as the treated group instead of German-filed patent presence.

In Table 6, I show the coefficients from regressing `Ten Year Count FR` on the same treated group (German-filed patent presence in a subclass) as done initially. From their coefficients and standard errors, both estimates are neither economically nor statistically different from zero.

\begin{table}[!htbp] \centering 
  \caption{Placebo DiD 1} 
  \label{model6.1_placebo} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & Ten Year Count USA \\ 
\hline \\[-1.8ex] 
 french\_presence & 0.004 \\ 
  & (0.043) \\ 
  & \\ 
 twea\_passed & 0.350$^{***}$ \\ 
  & (0.028) \\ 
  & \\ 
 placebo\_did\_french & 0.099 \\ 
  & (0.081) \\ 
  & \\ 
 Constant & 0.026$^{*}$ \\ 
  & (0.015) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,793 \\ 
R$^{2}$ & 0.066 \\ 
Adjusted R$^{2}$ & 0.065 \\ 
Residual Std. Error & 0.620 (df = 2789) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 


\begin{table}[!htbp] \centering 
  \caption{Placebo DiD 2} 
  \label{model6.1_placebo} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & Ten Year Count FR \\ 
\hline \\[-1.8ex] 
 treated\_group & 0.022$^{***}$ \\ 
  & (0.007) \\ 
  & \\ 
 twea\_passed & $-$0.002 \\ 
  & (0.010) \\ 
  & \\ 
 did & $-$0.015 \\ 
  & (0.014) \\ 
  & \\ 
 Constant & 0.012$^{**}$ \\ 
  & (0.005) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 2,793 \\ 
R$^{2}$ & 0.004 \\ 
Adjusted R$^{2}$ & 0.003 \\ 
Residual Std. Error & 0.166 (df = 2789) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

\newpage

## Question 7

These results are probably not generalizable to patents more broadly. This forfeiture of patent rights was an unanticipated "random" event that happened in wartime. It is because of this pseudo-randomness and transience that we can extrapolate from it; but if countries were routinely ignoring each other's patent laws, then the effects would likely decay. 

The results are probably more likely to generalize to older patents, those in certain sectors (biomedicine, manufacturing processes, STEM fields, and so on) than to more recent developments. It would make sense that opening up process-based patents would be more beneficial than some other more esoteric patents; with it, any firm could use (and improve upon) an existing patent, which could lead to more patents through some spillover effects.

For more cutting-edge patents (for example, MRNA vaccine production), opening up patents wouldn't be as beneficial &mdash; at least in the short term &mdash; since few companies in the world could replicate the technical process even if they had the legal rights to do so.

